Actuator line modeling of vertical-axis turbines

### 2016-05-04 paper.tex
Add blade chord line

    \caption{Vector diagram of velocity and forcing on a cross-flow turbine
    blade element. Note that the free stream velocity $U_\infty$ is from top to
    bottom (identical to $U_in$ for purely geometric calculations), the blade
    chord is in line with the tangential velocity (i.e., zero preset pitch,
    which would offset the geometric angle of attack $\alpha$), and the drag
    vector is magnified by a factor of two (approximately, relative to the lift
    vector) to enhance visibility.}

>>>>

    \caption{Vector diagram of velocity and forcing on a cross-flow turbine
        blade element. Note that the free stream velocity $U_\infty$ is from top to
        bottom (identical to $U_in$ for purely geometric calculations), the blade
        chord (dash-dotted line) is coincident with the tangential velocity (i.e.,
        zero preset pitch, which would offset the geometric angle of attack
        $\alpha$), and the drag vector is magnified by a factor of two
        (approximately, relative to the lift vector) to enhance visibility.}
